Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-13 paper.tex

Domesticated and wild barley belong to the same species, \emph{Hordeum vulgare}, and are capable of producing viable offpspring via hybridization \cite{von1995ecographical}.
Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) is believed to have been domesticated at least twice roughly 10,000 BP, once from wild subsp. \emph{spontaneum} in the Fertile Crescent and once from subsp. \emph{spontaneum} var. \emph{agriocrithon} in Tibet \cite{takahashi1955origin, badr2000origin, oka2012origin, azhaguvel2007phylogenetic, haberer2015barley}.
However, details of barley domestication are still disputed.

>>>>

Domesticated and wild barley belong to the same species, \emph{Hordeum vulgare}, and are capable of producing viable offpspring via hybridization \cite{von1995ecographical}.
Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) is believed to have been domesticated at least twice roughly 10,000 BP, once from wild subsp. \emph{spontaneum} in the Fertile Crescent and once from subsp. \emph{spontaneum} var. \emph{agriocrithon} in Tibet \cite{takahashi1955origin, badr2000origin, oka2012origin, azhaguvel2007phylogenetic, haberer2015barley}.
\gmj{the source morrell2007genetic will be used to update this paragraph once we've worked out for sure that the second domestication of barley was in the Zargos mountains, rather than Tibet.  Also, this paper puts the earliest archaeological samples of barley at closer to 8500 calibrated years ago.}
However, details of barley domestication are still disputed.
